Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-13 paper/section_5_experiments.tex
Merge linguistic and name metric tables

\begin{table}[t]
   \caption {Linguistic measures on the generated captions: caption length (CL),
             type-token ratio (TTR), and Flesch readability ease (FRE).}
	\label{tab:caption}
	\centering
	\begin{tabularx}{\linewidth}{llXXX}
		\toprule
       &  &  CL  & TTR & FRE \\
      \midrule
      \multirow{10}{*}{\rotatebox[origin=c]{90}{GoodNews}}
      & Ground Truths & 18.1 & 94.9 & 65.4 \\
      \cmidrule{2-5}
      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 92.2 & 78.3 \\
      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 &  \\
      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 &  \\
      % Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 &  \\
      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 &  \\
      & Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.1 & 90.7 & 77.6 \\
      \cmidrule{2-5}
      & Transformer + RoBERTa \\
      & LSTM + GloVe & 13.8 & 89.6 & 77.5 \\
      & Transformer + GloVe & 15.5 & 88.5 & 73.9 \\
      & LSTM + weighted RoBERTa &  &   \\
      \cmidrule{2-5}
      & \quad + weighted RoBERTa & 15.5 & 91.0 & 72.0 \\
      & \quad\quad + face attention & 15.5 & 90.7 & 71.9 \\
      & \quad\quad\quad + copy mechanism \\
      \midrule
      \multirow{9}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
      & Ground Truths & 18.4 & 94.6 & 63.9 \\
      & LSTM + GloVe  & 13.8 & 89.0 & 77.8 \\
      & Transformer + GloVe  & 15.1 & 88.6 & 73.8 \\
      & LSTM + weighted RoBERTa  & 14.9 & 90.2 & 72.6 \\
      \cmidrule{2-5}
      & Transformer + RoBERTa \\
      & \quad + weighted RoBERTa  & 15.3 & 91.5 & 70.4 \\
      & \quad\quad + location-aware & 15.1 & 91.7 & 70.4  \\
      & \quad\quad\quad + face attention & 15.2 & 91.6 & 70.5 \\
      & \quad\quad\quad\quad + copy mechanism \\
		\bottomrule
	\end{tabularx}
\end{table}

@@

Table \ref{tab:caption} look at the quality of the generated captions. We look
at three metrics: caption length, type-token ratio (TTR), and Flesch reading
ease. TTR is the ratio of the number of unique words to the total number of
words in a caption. The Flesch reading ease takes into account the number of
words and syllables and produces a score between 0 and 100, where higher means
being easier to read.

>>>>

@@

Table \ref{tab:names} also looks at the quality of the generated captions. We
look at three metrics: caption length, type-token ratio (TTR), and Flesch
reading ease. TTR is the ratio of the number of unique words to the total
number of words in a caption. The Flesch reading ease takes into account the
number of words and syllables and produces a score between 0 and 100, where
higher means being easier to read.
